%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Zhu Zelong} % Your name
\address{Mobile: +86 18022308628 \\ Email: zelong.zhu@icloud.com} % Your phone number and email
% \address{LinkedIn: \tt cn.linkedin.com/in/zhuzelong/en}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{education}

\begin{rSubsection}{The University of Manchester (UK)}{September 2014--September 2015}{}{}
    \item MSc in Advanced Computer Science: Knowledge and Data Management (Major in data science)
\end{rSubsection}

\begin{rSubsection}{Central University of Finance and Economics (China)}{September 2007--June 2011}{}{}
    \item Bachelor: Information Management and Information System
    \item Overall GPA: 3.5/4.5 (Rank: 2/29)
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{working experience}

\begin{rSubsection}{China Guangfa Bank}{July 2011--January 2014}{IT Department of Head Office}{Assistant of suppliers manager}
    \item Suppliers management:
    Searched for eligible suppliers of appliances, software, software development and maintenance for different projects. Maintained the data regarding suppliers, products and services.
    Investigated features of hardware and software.
    Negotiated prices with suppliers.
    \item Project management:
    Assessed the selections of appliances and system software based on budget, costs and features of products. Evaluated the periods of purchase to help make the project plans.
    I participated in the project of construction of the Nanhai data centre.
    \item Product evaluation:
    Helped developers to evaluate appliances and software. Participated in products conferences and make decisions on adoption of new products.
\end{rSubsection}

\end{rSection}



%----------------------------------------------------------------------------------------
%   PROJECT EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{project experience}

\begin{rSubsection}{Data mining in Bibliotheca}{Feb 2015 -- Sep 2015}{}{}
\item Analyzed the transactional data of libraries provided by Bibliotheca and compiled an analytical report.
\item Used MSSQL and R to clean data and preprocess data.
\item Used Python and Google API to reverse geocode the location of libraries.
\item Used R to carry out exploratory data analysis; implement time series analysis for prediction.
\item Used Python to carry out clustering and classification analysis; I also implemented a clustering algorithm and a feature selection algorithm in Python.
\item Compiled an analytical report. The report also served as my MSc dissertation.

\end{rSubsection}

\end{rSection}



%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{rSubsection}{}{}{}{}
\item {Python:} Familiar with Python in data analysis. Also capable of implementing algorithms in Python.
\item {R:} Familiar with R in data analysis and writing reports in R. Basic level in statistics.
\item {SQL:} Proficient in writing SQL queries to extract and transform data.
\item {\LaTeX{}:} Proficient in writing reports in \LaTeX{}.
\item{Git}: I used Git and Github to manage my project and coursework.
\item {Business communication:} I am experienced in communicating with and coordination.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
