%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Zhu Zelong} % Your name
% \address{Mobile: +44 (0) 7421 305652 \\ Email: \tt zelong.zhu@postgrad.manchester.ac.uk} % Your phone number and email
% \address{LinkedIn: \tt cn.linkedin.com/in/zhuzelong/en}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{education}

\begin{rSubsection}{The University of Manchester}{September 2014--September 2015}{}{}
    \item MSc in Advanced Computer Science: Knowledge and Data Management
    \item Course units: Machine learning, Advanced database management, Data engineering, Automated reasoning, Optimization for problem solving 
    \item MSc Project: Data mining in Bibliotheca
\end{rSubsection}

\begin{rSubsection}{Central University of Finance and Economics (China)}{September 2007--June 2011}{}{}  
    \item Bachelor of Management: Information Management and Information System
    \item Course units (partial):
        Calculus, Linear algebra, Probability and Statistics, Discrete mathematics; 
        C, Java programming, Data structure, Information system analysis and design, Database;  
        Accounting, Macro and micro economics
    \item Overall GPA: 3.5/4.5 (Rank: 2/29)
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{working experience}

\begin{rSubsection}{China Guangfa Bank}{July 2011--January 2014}{IT Department of Head Office}{Assistant of suppliers manager}
    \item Suppliers management:
    Searched for eligible suppliers of appliances, software, software development and maintenance for different projects. Maintained the data regarding suppliers, products and services.
    Investigated features of hardware and software.
    Negotiated prices with suppliers.
    \item Project management:
    Assessed the selections of appliances and system software based on budget, costs and features of products. Evaluated the periods of purchase to help make the project plans.
    I participated in the project of construction of the Nanhai data centre.
    \item Product evaluation:
    Helped developers to evaluate appliances and software. Participated in products conferences and make decisions on adoption of new products.
\end{rSubsection}

\end{rSection}



%----------------------------------------------------------------------------------------
%   PROJECT EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
%\begin{rSection}{project experience}

%\end{rSection}



%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Computer Languages & Prolog, Haskell, AWK, Erlang, Scheme, ML \\
%Protocols \& APIs & XML, JSON, SOAP, REST \\
%Databases & MySQL, PostgreSQL, Microsoft SQL \\
%Tools & SVN, Vim, Emacs
%\end{tabular}
\begin{rSubsection}{Technical Skills}{}{}{}
\item {Python:} I used Python to process data and carry out machine learning in my MSc project. 
\item {R:} I took R courses on Coursera and use R to carry out data analysis in my MSc project.
\item {MS SQL Server:} I used MSSQL to carry out data wrangling in my MSc project, I am able to write SQL for data transformation.
\item {\LaTeX:} I wrote essays and thesis with {\LaTeX} during my MSc courses. 
\item{Git}: I used Git and Github to manage my code (including coursework and MSc project).
\item {Business communication:} I am experienced in communicating with and coordinating business departments and suppliers.
\end{rSubsection}


\begin{rSubsection}{Language}{}{}{}
\item{English:} Good user (IELTS 7.5). I am able to talk with technicians in English and to write business email
\item{Chinese:} Native Speaker of Mandarin and Cantonese
\item{French:} Elementary (studied over 400 hours, approximately A2)
\end{rSubsection}



\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
